ext_risk_copula

### 2019-01-29 ext_risk_copula.Rmd
adding msmith result with scl=0.8

```{r fig_msmith, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

model<-"msmith"

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-4
scl<-1

@@

# plot for global dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

```{r fig_msmith_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
msmith_extrisk_d0<-readRDS("./Results/msmith/msmith_extrisk_d0.RDS")

msmith_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims
msmith_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims

@@

pdf("./Results/msmith/msmith_extrisk_d0.pdf",height = 6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0.8,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/msmith/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/msmith/msmith_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model with no dispersion : rc=4/3); numlocs=5, numsteps=25, numsims=10000\label{fig_msmith_risk_d0}](./Results/msmith/msmith_extrisk_d0.pdf){ width=40%, height=40% }

@@

>>>>

```{r fig_msmith_scl_1, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

model<-"msmith"
scl<-1

tempo<-paste("./Results/",model,"_scl_",scl,sep="")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-4

@@

# plot for global dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# Plot ext_risk_d0
msmith_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims
msmith_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/msmith_scl_1/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/msmith_scl_1/msmith_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model with no dispersion : rc=4/3); numlocs=5, numsteps=25, numsims=10000\label{fig_msmith_risk_d0}](./Results/msmith_scl_1/msmith_extrisk_d0.pdf){ width=40%, height=40% }

```{r fig_msmith_scl_0.8, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

model<-"msmith"
scl<-0.8

tempo<-paste("./Results/",model,"_scl_",scl,sep="")
if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-4

# plot for global dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# Plot ext_risk_d0
msmith_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims
msmith_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=msmith_extrisk_d0$risk_left_d0)/numsims

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3, scl=0.8) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary_scl_0.8}](./Results/msmith_scl_0.8/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model : a = 1, b = 3, rc = 4/3, scl=0.8) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary_scl_0.8}](./Results/msmith_scl_0.8/msmith_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model with no dispersion : rc=4/3, scl=0.8); numlocs=5, numsteps=25, numsims=10000\label{fig_msmith_risk_d0_scl_0.8}](./Results/msmith_scl_0.8/msmith_extrisk_d0.pdf){ width=40%, height=40% }

@@

# Austin Brewer model :
